\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{tipa}
\usepackage{vowel}
\usepackage{phonrule}
\usepackage{qtree}
\usepackage{listings}
\lstset{language=Python}
\usepackage{xcolor}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle} 
 
 
\title{Latex Project 2}
\author{Martyna Iwaniec I MA PJN}
\date{April 2020}

\begin{document}

\maketitle

\section{Task One}

\subsection{English}
\textipa{
/aIm @ "stju:d@nt @t ju:nI"v\textrevepsilon{}:sIti @v "gd\textturnv{}nsk. aIm "st\textturnv{}dIN "n\ae{}\textteshlig{}r@l "l\ae{}NgwI\textdyoghlig{} "pr@UsEsIN @t ði "InstItju:t @v "INglI\textesh{} @nd @"mErIk@n "st\textturnv{}diz. "k\textturnv{}r@ntli, aIm "du:Iŋ maI "k\textopeno{}:sIz "OnlaIn, bI"k@z ð@ h@Ul w\textrevepsilon{}:ld Iz In "kwOr@nti:n. "evri deI, aI dU maI "h@Umw\textrevepsilon{}:k, kUk @nd "lIsn t@ "mju:zIk. wOt Iz mO: aI mIs "n\textopeno{}:m@l laIf @nd "bi:IN aUt"saId/}

\subsection{Polski}
\textipa{ \hfill \break
/"jE{\|[s}{\|[t}Em {\|[s}{\|[t}U"{\|[d}e{\|[n}{\|[t}kOm U{\|[n|}IvErs1"{\|[t}E{\|[t}U g{\|[d}a\textltailn{}{\|[s}"kIEgO. {\|[s}{\|[t}U"{\|[d}jUjE p\textesh{}EtfaZa{\|[n}jE jE{\|[n}"z1ka {\|[n}atUral"{\|[n}EgO v  I{\|[n}{\|[s}{\|[t}1"{\|[t}U\t\texttctclig{}E a{\|[n}g"lI{\|[s}{\|[t}1kI I amer1ka"{\|[n}I{\|[s}{\|[t}1kI. O"bE\t{\|[t\|[s}{\|[n}je "robjE "kUr{\|[s}1 O{\|[n}"laI{\|[n} bO "\t{\|[t\|[s}aw1 "\textctc{}vja{\|[t} "jE{\|[s}{\|[t} pO{\|[d} kfara{\|[n}"{\|[t}a{\|[n}{\|[n}Om. kaZ"{\|[d}EgO {\|[d}{\|[n}ja "rObjE "pracE {\|[d}O"mOvE, gO"{\|[t}UjE I "{\|[s}wUxam mU"z1kI. \t{\|[t\|[s}O "vjEn\texttslig{}Ej, "{\|[t}E{\|[n}{\|[s}k{\|[n}jE za {\|[n}Or"mal{\|[n}1m "Z1\t\texttctclig{}Em I "b1\t\texttctclig{}Em {\|[n}a "{\|[d}vOZE/ }

\section{Task Two}
Temne language:

\begin{vowel}
\putvowel[l]{\textipa{i}}{16pt}{8pt}
\putvowel[r]{\textipa{e}}{20pt}{25pt}
\putvowel[r]{\textipa{\textepsilon}}{31pt}{35pt}
\putvowel[l]{\textipa{\textschwa}}{50pt}{26pt}
\putvowel[r]{\textipa{\textturnv}}{54pt}{38pt}
\putvowel[l]{\textipa{o}}{76pt}{28pt}
\putvowel[l]{\textipa{u}}{76pt}{12pt}
\putvowel[r]{\textipa{a}}{57pt}{52pt}
\putvowel[r]{\textipa{\textopeno}}{68pt}{38pt}

\end{vowel}

\section{Task Three}
A phonological rule - tapping:

\phonb
{\phonfeat{+alveolar \\ +stop } }
{[\textfishhookr]} {\phonfeat{+syllabic \\ +stressed} }{\phonfeat{+syllabic \\ -stress} }

\section{Task Four}
A syntactic tree:
Happy linguists made a tree.
\Tree [.S [.NP [.Adj happy ] [.N linguists ] ] [.VP [.V made ] [.NP [.det a ] [.N tree ] ] ] ]


\section{Task Five}
********* Source Code Listings *********
\begin{lstlisting}

def is_key(dictionary, key):
    if key in dictionary:
        return True
    else:
        return False
\end{lstlisting}
\end{document}
